---
title: "Four Parameters:Categorical"
author: "Ansh Kare"
format: html
execute:
        echo: false
---


We created a preceptor table with the data that we are looking for. We then pulled data from nes, and used the 1992 voting responses for a our data of a population table. We are looking to answer the question, whether sex affects voter behavior for the 1992 presidential election. We took the data, and questions whether the data is representative, random, and not biased. We created a Data generating mechanism to predict the values and see the relationship between gender and voter behavior. We found out the Male were less likely to vote for Clinton and more likely to vote for Perot, and women were more likely to vote for Clinton. After creating the DGM, we used the posterior results to create graphs to depict how voter behavior was influence by gender in each candidate.
```{r}
#| label: setup
#| message: FALSE
library(primer.data)
library(tidyverse)
library(tidybayes)
library(brms)
library(gtsummary)
```
```{r}
#| label: cleaning
#| message: FALSE
nes_92<-nes |> 
  filter(year == 1992) |>
  select(pres_vote, sex) |>
  drop_na() |> 
  mutate(pres_vote = case_when(
    pres_vote == "Democrat" ~ "Clinton",
    pres_vote == "Republican" ~ "Bush",
    pres_vote == "Third Party" ~ "Perot"
  ))
```
\begin{aligned}
\rho_{clinton} &=& \frac{e^{\beta_{0, clinton} + \beta_{1, clinton} male}}{1 + e^{\beta_{0, clinton} + \beta_{1, clinton} male}}\\
\rho_{perot} &=& \frac{e^{\beta_{0, perot} + \beta_{1, perot} male}}{1 + e^{\beta_{0, perot} + \beta_{1, perot} male}}\\
\rho_{bush}  &=& 1 - \rho_{clinton} - \rho_{perot}
\end{aligned}
```{r}
#| label: model
#| cache: true
fit_nes<-brm(formula = pres_vote~sex, data = nes_92, family = categorical(), silent = 2, refresh = 0, seed = 76)

```

```{r}
#| label: table
tbl_regression(fit_nes)

```

```{r}
#| label: plot
newdata<- tibble(sex = c("Female", "Male"))
ndata <- tibble(sex = c("Female", "Male"))

fit_nes|> add_epred_draws(newdata = ndata)|> select(sex, .category, .epred)|>
ggplot(aes(x = .epred, fill = sex))+
geom_histogram(bins = 100)+
facet_grid(~.category)+
scale_x_continuous(breaks =c(0.05, 0.3, 0.6), labels = scales::percent_format() )+
labs(title = "Posterior for exprected probability of Candidate support based on Gender", subtitle = "Women are most likely to support Clinton", x = "Expected probability", y = "count")
```
